HERMES: Hybrid Error-corrector Model with inclusion of External Signals for nonstationary fashion time series

### 2023-01-26 tmlr_submission/hermes_paper_submission/hermes_paper.tex
change sections order and add a figure

In this paper, we consider an emerging time series forecasting application referred to as {\em fashion trends prediction}. In fashion and retails industries, accurately anticipating consumers' needs is vital and wrong decisions can lead to massive wastes. With the explosion of social network and the recent advances in image recognition, it is possible to translate the visibility of fashion items on social media over time into time series. Consequently, models and algorithms can be trained to accurately anticipate and predict consumer behaviour. In \citet{ma2020}, a  dataset is provided using social media pictures and an image recognition framework to detect several clothes: 2000 fashion time series are proposed with a weekly seasonality. However, only 3 years of historical data is available (144 data points) that may not be sufficient for some statistical approaches. In \citet{ma2020}, another dataset is presented gathering 8000 fashion sequences with an historical available data  increased to 5 years. Nevertheless, only 120 values are available for each fashion time series and the overall volume remains low for a large part of the sequences resulting in a lot of noise and no clear patterns. In this paper, we propose a new fashion dataset overcoming the weaknesses of the two previous ones. Based on cutting-edge image recognition algorithms \citep{ren2015,chollet2017}, we built a large fashion dataset containing \numberts\ weekly sequences of fashion trends on social media with 5 years of historical data from 01-01-2015 to 30-12-2019. This dataset has very appealing properties:  all time series have the same length (261 data points), there is no missing value and there is no sparse time series even for niche trends. Concerning fashion dynamics, some of them appear to be really volatile with nonlinear changes of dynamics resulting from the emergence of new tendencies. In this context, understanding early signals of the apparition of a trend is one of the key to accurately forecast the future of the fashion. Consequently, the originality of our dataset comes from the fact that additional external weak signals are introduced. With our fashion expertise, we detected several groups of highly influential fashion users. Analyzing their specific behaviours on social media, we associate with each time series an external weak signal representing the same fashion trends on a sub-category of users. They are called weak signals because they are often alerts or events that are too sparse, or too incomplete to allow on their own an accurate estimation of their impact on the prediction of the target signal. Figure \ref{fig:oneemergingtrend} shows an example of fashion time series with its linked influencers weak signal. Exploring this new way of representing fashion, we aim at designing a model able to deal with such a large dataset, leveraging  complex external weak signals and finally providing the most accurate forecasts.

@@

The paper is organized as follows. Section~\ref{sec:hybrid} introduces the proposed hybrid model. Then, the new fashion dataset provided with this article is presented in Section~\ref{sec:dataset}. Section~\ref{sec:exp} describes the HERMES results and comparisons with several benchmarks. Finally, a general conclusion and some research perspectives are given in  Section~\ref{sec:conclusion}.

@@

\section{Hybrid model with external signals}
\label{sec:hybrid}
We introduce a new hybrid approach for time series forecasting  composed of two parts: a collection of per-time-series parametric models, and a global error-corrector neural network train on all time series. Per-time-series parametric models are used to learn local behaviours, to normalize sequences by removing trends and seasonality,  and to compute a first forecast. Then, gathering information of the first predictions and external variables, a recurrent neural network is trained to correct the predictions provided by the first collection of per-time-series models.

@@

section{Fashion dataset with external weak signals}
\label{sec:dataset}

The 150 million of social media pictures are analyzed with the visual recognition pipeline described below. Out of those images, we detected clothes in 96 millions posts making the final dataset used in this paper. We aggregate results by fashion trend definition over the time and  thousands of trends are finally translated from social media to time series. We note $y^{c,g,m,i}$ the final raw sequence representing the fashion trend $i$ of the cloth type $c$ for the gender $g$ on market $m$. At each time t, $y^{c,g,m,i}_t$ represents the number of posted pictures in the market $m$ during the week $t$ where computer vision algorithms detected the fashion trend $i$ of the cloth type $c$ for the gender $g$.

As an illustration, an example of fashion time series is given in Figure~\ref{fig:oneemergingtrend}.

\subsection{Fashion time series}
\label{sec:dataset:b}

Due to the increasing use of social media and continuous changes of users' behaviours, a normalization step is applied to the raw sequences in order to remove bias. Thus, we define the following normalizing signal $\Tilde{y}^{c,g,m}$. This signal represents the global sequence of the cloth type $c$ for the gender $g$ on market $m$ (e.g the evolution of the skirts in general for female in Europe). With the R package \texttt{stats}, the Seasonal-Trend decomposition using LOESS  \citep{cleveland1990} is used to remove the seasonal component of $\Tilde{y}^{c,g,m}$. The resulting deseasonalized signal is called  $\bar{y}^{c,g,m}$. Finally, for any fashion trend $i$, the following normalized sequence is defined for all $ 0 \leq t \leq T$:
\begin{equation}
    y^{i}_t = \frac{y^{c,g,m,i}_{t}}{\bar{y}^{c,g,m}_t}\,,
\end{equation}
where T denotes the number of available time steps. The time series $y^{c,g,m,i}$ is divided by the deseasonalized signal $\bar{y}^{c,g,m}$ and not $\Tilde{y}^{c,g,m}$ in order to avoid removing the seasonality of all the fashion trend sequences. With this normalizing step, a majority of the social media bias are removed and the final normalized sequences are expressed in share of category. As an illustration, an example of the normalization process is displayed in Figure~\ref{fig:normalization}. The raw Jersey Top trend for females in China is divided by the deseasonalized global Top trend for females in China.

>>>>

In this paper, we consider an emerging time series forecasting application referred to as {\em fashion trends prediction}. In fashion and retails industries, accurately anticipating consumers' needs is vital and wrong decisions can lead to massive wastes. With the explosion of social network and the recent advances in image recognition, it is possible to translate the visibility of fashion items on social media over time into time series. Consequently, models and algorithms can be trained to accurately anticipate and predict consumer behaviour. In \citet{ma2020}, a  dataset is provided using social media pictures and an image recognition framework to detect several clothes: 2000 fashion time series are proposed with a weekly seasonality. However, only 3 years of historical data is available (144 data points) that may not be sufficient for some statistical approaches. In \citet{ma2020}, another dataset is presented gathering 8000 fashion sequences with an historical available data  increased to 5 years. Nevertheless, only 120 values are available for each fashion time series and the overall volume remains low for a large part of the sequences resulting in a lot of noise and no clear patterns. In this paper, we propose a new fashion dataset overcoming the weaknesses of the two previous ones. Based on cutting-edge image recognition algorithms \citep{ren2015,chollet2017}, we built a large fashion dataset containing \numberts\ weekly sequences of fashion trends on social media with 5 years of historical data from 01-01-2015 to 30-12-2019. This dataset has very appealing properties:  all time series have the same length (261 data points), there is no missing value and there is no sparse time series even for niche trends. Concerning fashion dynamics, some of them appear to be really volatile with nonlinear changes of dynamics resulting from the emergence of new tendencies. In this context, understanding early signals of the apparition of a trend is one of the key to accurately forecast the future of the fashion. Consequently, the originality of our dataset comes from the fact that additional external weak signals are introduced. With our fashion expertise, we detected several groups of highly influential fashion users. Analyzing their specific behaviours on social media, we associate with each time series an external weak signal representing the same fashion trends on a sub-category of users. They are called weak signals because they are often alerts or events that are too sparse, or too incomplete to allow on their own an accurate estimation of their impact on the prediction of the target signal. Exploring this new way of representing fashion, we aim at designing a model able to deal with such a large dataset, leveraging  complex external weak signals and finally providing the most accurate forecasts.

@@

The paper is organized as follows. Section~\ref{sec:dataset} presents the new fashion dataset provided with this article. Then, the proposed forecasting approach HERMES is presented in Section~\ref{sec:hybrid}. Section~\ref{sec:exp} describes the model results and comparisons with several benchmarks on the 2 different use cases: the fashion dataset and the M4 competition weekly dataset. Finally, a general conclusion and some research perspectives are given in  Section~\ref{sec:conclusion}.

\section{From social media to fashion time series}
\label{sec:dataset}

\begin{figure*}
  \centering
    \includegraphics[width=1.\linewidth]{pipeline_archi}
  \caption{From social media to fashion time series. a) A complete image dataset of 150 millions of pictures is collected from social media users localized on 5 strategic markets. b) A visual recognition pipeline is applying on images. Global fashion items are detected with a collection of fine-grain attributes. c) Result are aggregated by fashion trend definition over the time and normalized in order to remove social media bias. The fashion time series are created.}
\label{fig:pipeline}
\end{figure*}

The 150 million of social media pictures are analyzed with the visual recognition pipeline described below. Out of those images, we detected clothes in 96 millions posts making the final dataset used in this paper. We aggregate results by fashion trend definition over the time and  thousands of trends are finally translated from social media to time series. We note $y^{c,g,m,i}$ the final raw sequence representing the fashion trend $i$ of the cloth type $c$ for the gender $g$ on market $m$. At each time t, $y^{c,g,m,i}_t$ represents the number of posted pictures in the market $m$ during the week $t$ where computer vision algorithms detected the fashion trend $i$ of the cloth type $c$ for the gender $g$. As an illustration, an example of fashion time series is given in Figure~\ref{fig:oneemergingtrend}.

@@

\subsection{Removing social media bias}
\label{sec:dataset:b}

Due to the increasing use of social media and continuous changes of users' behaviours, a normalization step is applied to the raw sequences $y^{c,g,m,i}$ in order to remove bias. Thus, we define the following normalizing signal $\Tilde{y}^{c,g,m}$. This signal represents the global sequence of the cloth type $c$ for the gender $g$ on market $m$ (e.g the evolution of the skirts in general for female in Europe). With the R package \texttt{stats}, the Seasonal-Trend decomposition using LOESS  \citep{cleveland1990} is used to remove the seasonal component of $\Tilde{y}^{c,g,m}$. The resulting deseasonalized signal is called  $\bar{y}^{c,g,m}$. Finally, for any fashion trend $i$, the following normalized sequence is defined for all $ 0 \leq t \leq T$:
\begin{equation}
    y^{i}_t = \frac{y^{c,g,m,i}_{t}}{\bar{y}^{c,g,m}_t}\,,
\end{equation}
where T denotes the number of available time steps. The time series $y^{c,g,m,i}$ is divided by the deseasonalized signal $\bar{y}^{c,g,m}$ and not $\Tilde{y}^{c,g,m}$ in order to avoid removing the seasonality of all the fashion trend sequences. With this normalizing step, a majority of the social media bias are removed and the final normalized sequences are expressed in share of category. As an illustration, an example of the normalization process is displayed in Figure~\ref{fig:normalization}. The raw Jersey Top trend for females in China is divided by the deseasonalized global Top trend for females in China.

\section{The HERMES approach: a new hybrid model for time series forecasting}
\label{sec:hybrid}
We introduce a new hybrid approach for time series forecasting  composed of two parts: a collection of per-time-series parametric models, and a global error-corrector neural network train on all time series. Per-time-series parametric models are used to learn local behaviours, to normalize sequences by removing trends and seasonality,  and to compute a first forecast. Then, gathering information of the first predictions and external variables, a recurrent neural network is trained to correct the predictions provided by the first collection of per-time-series models.

@@
